---
title: "Quiz1"
author: "Natalie Robinson"
date: "September 26, 2017"
output: html_document
---

# QUIZ 1
Import zombies.csv
```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

create a new data frame with the first/last name of all female survivors using 'piping' %>%
```{r}
library(dplyr)
newd <- filter(d, gender == "Female") %>%
  select(first_name, last_name)
newd
```

# QUIZ 2

I was absent this day

# QUIZ 3

Import zombie data
```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

Filter medical/nursing majors
```{r}
library(dplyr)
newdata <- filter(d, major == "medicine/nursing")
newdata
```

What is the relationship between age and years of education (years of education is a continuous variable)

Plot this relationship as a scatter plot with a regression line with 95% confidence intervals
Color the points so that males are pink and females are blue

```{r}
library(ggplot2)

# standard plot of the data (age by years of education)
m <- plot(newdata$years_of_education ~ newdata$age)
m
```

```{r}
# linear model of the data

m <- lm(data = newdata, age ~ years_of_education)
m

ci <- confint(m, level = 0.95)
ci

ci <- predict(m, newdata, interval = "confidence", level = 0.95)
head(ci)

df <- cbind(ci)
names(df) <- c("x", "y", "yhat", "CIfit", "CIlwr", "CIupr")
head(df)

g <- ggplot(data = newdata, aes(x = years_of_education, y = age))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g <- g + geom_line(aes(x = x, y = CIfit), colour = "black")
g <- g + geom_line(aes(x = x, y = CIlwr), colour = "blue")
g <- g + geom_line(aes(x = x, y = CIupr), colour = "blue")
g <- g + geom_point(newdata$female, aes(colour = "blue"))
g
```



